%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Andrew Cheng} \\ \vspace{1pt}
    \small 516-984-2651 $|$ \href{mailto:andrew.cheng.2@stonybrook.edu}{\underline{andrew.cheng.2@stonybrook.edu}} $|$ 
    \href{https://www.linkedin.com/in/andrew-cheng-84a6392b5/}{\underline{linkedin.com/in/andrew-cheng-84a6392b5}} $|$
%    \href{https://github.com/...}{\underline{github.com/jake}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Stony Brook University}{Stony Brook, NY}
      {Bachelor of Science in Computer Science}{Aug. 2024 -- May 2028}
    \resumeSubheading
      {East Meadow High School}{East Meadow, NY}
      {High School Diploma}{Sept. 2020 -- June 2024}

    \resumeItemListStart
    \resumeItem{Salutatorian (Rank 2/390)}   
      \resumeItem{National Merit Finalist, AP Scholar with Distinction, American Mathematics Competition Award}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {STEM Instructor}{July 2023 -- Aug. 2024}
      {Mathnasium}{Levittown, NY}
      \resumeItemListStart
        \resumeItem{Tutored 20+ weekly students in Geometry, Algebra 1-2, Pre-Calculus, AP Calculus, AP Chemistry, Statistics, \& Computer Science.
}
        \resumeItem{Designed summer programs preparing students for the AMC/AIME, and developing beginner programming skills in Python.
        }
        \resumeItem{Developed a system to transfer contact information of 500+ parents from scanned documents into Google Sheets and import to Google Contacts.
        }
    \resumeItemListEnd

    \resumeSubheading
      {IMC Prosperity Competitor}{Apr. 2024}
      {IMC Trading}{Remote}
      \resumeItemListStart
        \resumeItem{Competed in IMC's Prosperity Trading Challenge, a 15-day global competition with a \$50,000 prize pool, with simulated trading scenarios across five rounds.
        }
        \resumeItem{Collaborated with a team to develop Python trading algorithms, leveraging analytical skills.
        }
        \resumeItem{Applied probability distributions, game theory, and calculus to optimize strategy in manual trading rounds.
        }
        \resumeItem{
        Placed top 500 placement internationally out of 13,000 participants including top university students and industry professionals from firms like Citadel and D.E. Shaw.
        }
    \resumeItemListEnd
    
    \resumeSubheading
      {Python Program Director}{Jan. 2024 - Apr. 2024}
      {East Meadow Public Library}{East Meadow, NY}
      \resumeItemListStart
        \resumeItem{Proposed and headed weekly introductory programming program at EM Public Library for middle school students.
        }
        \resumeItem{Created a comprehensive curriculum tailored for beginners, covering fundamental programming concepts in Python/NumPy.
        }
        \resumeItem{Structured a series of interactive sessions that included hands-on coding exercises, projects, and assessments
        }
        \resumeItem{Managed program logistics, such as scheduling, venue setup, and participant enrollment.
        }
        \resumeItem{Analyzed participant progress and outcomes, adapting the curriculum to better meet learners' needs.
        }
        \resumeItem{Fostered relationship with local schools to promote the program to more students in the community.
        }
      \resumeItemListEnd
  
    \resumeSubheading
    {President, Captain}{Oct. 2021 - Jun 2024}
    {Mu Alpha Theta Math Honor Society}{East Meadow, NY}
    \resumeItemListStart
        \resumeItem{Led an organization with 100+ members dedicated to learning and using math to benefit the community in three sectors: Peer Tutoring, Community Connections, and Math Team.
        }
        \resumeItem{
            Created free monthly SAT Bootcamp that leveraged practice test data to tailor a curriculum for 40+ students.
        }
        \resumeItem{
        Facilitated district-wide STEM Night by organizing 60+ volunteers into 30+ activities promoting K-6 STEM engagement including creating magnetic slime and programming Ozobots.
        }
        \resumeItem{
        First individual top 10 at the Nassau Math Tournament. Led team to top 10 in Nassau Math Tournament, top 5 in NCIML, and brought first 5 members to compete at ARML/NYSML as part of Nassau County All Star Team (Top 50 in county).
        }
        
        \resumeItem{
        Used Overleaf and LaTex to create handouts that were correlated with a 15\% increase in average scores on the AMC.
        }
    \resumeItemListEnd



    
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\begin{comment}
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
            \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
            \resumeItem{Visualized GitHub data to show collaboration}
            \resumeItem{Used Celery and Redis for asynchronous tasks}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
          \resumeItemListStart
            \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
            \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
            \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
            \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\end{comment}



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills/Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, JavaScript, HTML/CSS, Java, Python, LaTex  } \\
%     \textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI} \\
     \textbf{Developer Tools}{: Git, VS Code, Visual Studio, Netlify, Overleaf} \\
%     \textbf{Libraries}{: pandas, NumPy, Matplotlib}
    \textbf{Interests}{: Competitive Programming, Contest Math, Teaching, Running, Poker, Anime, Music, Teamfight Tactics}
    }}
 \end{itemize}


%-------------------------------------------

\end{document}